Appendix S1: Supporting Tables and Figures.

### 2022-07-27 ms/SI.Rmd

---
title: "Appendix S1: Supporting Tables and Figures."
geometry: margin=1in
link-citations: yes
csl: templates/american-journal-of-botany.csl
bibliography: leaf_disc.bib
fontsize: 12pt
header-includes:
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{colortbl}
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \usepackage[default]{sourcesanspro}
  - \usepackage{sourcecodepro}
  - \fancypagestyle{plain}{\pagestyle{fancy}}
  - \fancyhead[RE,RO]{Maenpuen \textit{et al}. --American Journal of Botany-- Appendix S1}
output:
  html_document:
    fig_caption: yes
    theme: spacelab #readable #sandstone #spacelab #flatly
    highlight: pygments #tango #kate
    toc: TRUE
    toc_depth: 2
    number_sections: FALSE
    toc_float:
      collapsed: TRUE
      smooth_scroll: TRUE
      toc: true
  bookdown::pdf_document2:
    citation_package: default
    toc: yes
    number_sections: no
    fig_caption: no
    keep_tex: yes
    # template: templates/eisvogel2.tex
---

@@

Generalization for a relationship between ratios of disc-based and whole-leaf estimates of leaf mass per area (LMA), leaf tissue density (LD), and leaf thickness (LT).
For the *i* tree individual or species, the relationship between ratios of disc-based and whole-leaf estimates of LMA, LD, and LT is:

$$
\frac{LDd_i}{LDw_i} = \frac{LMAd_i}{LMAw_i} \frac{LTw_i}{LTd_i}
$$

@@

$$
\frac{LDd_i}{LDw_i} = \frac{LMAd_i}{LMAw_i} exp(\epsilon_i) \;\;\;\;\epsilon_i \sim N(0, \sigma^2).
$$

@@

As we expected LD, showed the slightly smaller *R^2^* value than LMA (Figure below) in the Yunnan dataset.
We have independent measurement for thickness for leaf discs and whole-leaves in the Yunnan dataset.
If we use the same leaf thickness values for leaf discs and whole-leaves (i.e., LTw~i~/LTd~i~ =1), the scatter plots will be identical for LMA and LD.
Consequently, we do not perform further analyses for LD, because differences between whole-leaf LD and leaf disc LD only depends on the ratio between whole-leaf LMA and leaf disc LMA and measurement errors of leaf thickness.

@@

Standardized regression coefficients modelig the effects of leaf tissue density,
leaf area,
leaf thickness,
punch size, and
their interactios
(a) on the mean estimates of whole-leaf LMA, and
(b) on the estimated variance of whole-leaf LMA.
The leaf disc LMA was used for the baseline mean of the whole-leaf LMA.
Thick and thin lines indicate 90% and 95% credible intervals, respectively.
Circles show posterior means of coefficients.
Circles filled with blue indicate significant effects and white indicate non-significance effects.

@@

Relationships between species mean leaf mass per area (LMA) determined by using whole-leaves and leaf discs for species obtained with leaf punches of different diameters.
Dashed lines indicate 1:1 lines.
Blue solid lines indicate standardized major axis (SMA) regressions.
The 95% confidence intervals are resented as the shaded area.
The correlation is significant (*P* < 0.001).

![](../figs/sma_sep.pdf){ width="400" style="display: block; margin: 0 auto" }

@@

Relationships between whole-leaf LMA : disc leaf LMA and total dry mass for the leaf disc.
The relationships was heteroscedastic (unequal variance, *p* < 0.001; all the samples were analyzed together).
Samples with small total dry mass tended to show greater variance.

![](../figs/ratio_dm.pdf){ width="400" style="display: block; margin: 0 auto" }

>>>>

---
title: "Appendix S1: Supporting Tables and Figures."
geometry: margin=1in
link-citations: yes
csl: templates/american-journal-of-botany.csl
bibliography: leaf_disc.bib
fontsize: 12pt
header-includes:
  - \usepackage{float}
  - \usepackage{caption}
  - \usepackage{booktabs}
  - \usepackage{colortbl}
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \usepackage[default]{sourcesanspro}
  - \usepackage{sourcecodepro}
  - \fancypagestyle{plain}{\pagestyle{fancy}}
  - \fancyhead[RE,RO]{Maenpuen \textit{et al}. --American Journal of Botany-- Appendix S1}
output:
  html_document:
    fig_caption: yes
    theme: spacelab #readable #sandstone #spacelab #flatly
    highlight: pygments #tango #kate
    toc: TRUE
    toc_depth: 2
    number_sections: FALSE
    toc_float:
      collapsed: TRUE
      smooth_scroll: TRUE
      toc: true
  bookdown::pdf_document2:
    citation_package: default
    toc: yes
    number_sections: no
    fig_caption: no
    keep_tex: yes
  bookdown::word_document2:
    citation_package: default
    toc: yes
    number_sections: no
    fig_caption: no
---

@@

Generalization for a relationship between ratios of disc-based and whole-leaf-based estimates of leaf mass per area (LMA), leaf tissue density (LD), and leaf thickness (LT).
For the *i* tree individual or species, the relationship between ratios of disc-based and whole-leaf estimates of LMA, LD, and LT is:

$$
\frac{\mathrm{LD_d}_i}{\mathrm{LD_w}_i} = \frac{\mathrm{LMA_d}_i}{\mathrm{LMA_w}_i} \frac{\mathrm{LT_w}_i}{\mathrm{LT_d}_i}
$$

@@

$$
\frac{\mathrm{LD_d}_i}{\mathrm{LD_w}_i} = \frac{\mathrm{LMA_d}_i}{\mathrm{LMA_w}_i} exp(\epsilon_i) \;\;\;\;\epsilon_i \sim \mathcal{N}(0, \sigma^2).
$$

@@

As we expected LD, showed the slightly smaller *R*^2^ value than LMA (Figure below) in the Yunnan dataset.
We have independent measurement for thickness for leaf discs and whole-leaves in the Yunnan dataset.
If we use the same leaf thickness values for leaf discs and whole-leaves (i.e., LT~w*i*~/LT~d*i*~ = 1), the scatter plots will be identical for LMA and LD.
Consequently, we do not perform further analyses for LD, because differences between whole-leaf LD and leaf disc LD only depends on the ratio between whole-leaf LMA and leaf disc LMA and measurement errors of leaf thickness.

@@

Standardized regression coefficients modeling the effects of leaf tissue density,
leaf area,
leaf thickness,
punch size, and
their interactions on
(a) the mean estimates of whole-leaf-based leaf mass per area (LMA) and
(b) the estimated variance of whole-leaf LMA.
The leaf disc LMA was used for the baseline mean of the whole-leaf LMA.
Thick and thin lines indicate 90% and 95% credible intervals, respectively.
Circles show posterior means of coefficients.
Circles filled with blue indicate significant effects and white indicate non-significance effects.

@@

Relationships between species mean leaf mass per area (LMA) determined by using whole leaves and leaf discs obtained with leaf punches of different diameters.
Dashed lines indicate 1:1 lines.
Blue solid lines indicate standardized major axis (SMA) regressions.
The 95% confidence intervals are resented as the shaded area.
The correlation is significant (*P* < 0.001).

![](../figs/sma_sep.pdf){ width=400 margin=auto }

@@

Relationships between the ratio of whole-leaf leaf mass per area (LMA) to disc leaf LMA and total dry mass for the leaf disc.
The relationships was heteroscedastic (unequal variance, *p* < 0.001; all the samples were analyzed together).
Samples with small total dry mass tended to show greater variance.

![](../figs/ratio_dm.pdf){ width=400 margin=auto }
